Testable normative theories

### 2020-06-01 simple.tex
Phrased claim that looks plausibly adequate wrt validity and falsification; plus some discussion

\subsection{Validity and conditions}
\begin{definition}[Validity]
	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
\end{definition}

$\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any. (Actually any attacked may still attack the addition, but that’s because of some other not-yet-attacked, anticipated, attack.)

@@

>>>>

\subsection{Validity}
\begin{definition}[Validity]
	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
\end{definition}

\subsection{Discussion}
$\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any. (Actually any attacked may still attack the addition, but that’s because of some other not-yet-attacked, anticipated, attack.)

@@

There must exist a sequence $\ar_0, \ar_2, \ar_4, …$ such that $\ar_0$ is defended by $\ar_2$, and so on.

\subsection{Conditions with history}
$S_4$ defends $S_2$ under protection of $S_6$ iff: $[\exists \hist, \ar_3 \suchthat \hist, \ar_2, \ar_3 \ileadstoe ¬\phi] ⇒ [\forall \hist \suchthat \set{\ar_5 \suchthat f(\ar_5, \ar_4) \cap \args_6 ≠ \emptyset} \cap \hist = \emptyset: \hist, \ar_4 \ileadstoe \phi]$. No, my condition is about defending when required, so just need to defend in the sense: $\forall \hist \suchthat \set{\ar_5 \suchthat f(\ar_5, \ar_4) \cap \args_6 ≠ \emptyset} \cap \hist = \emptyset: \hist, \ar_4 \ileadstoe \phi$. This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \phi$ to falsify the theory.

$\ar_4$ defends $\phi$ under protection of $S_6$ iff: $\forall \hist \in \allhist \suchthat \set{\ar_5 \in \allargs \suchthat f(\ar_5, \ar_4) \cap \args_6 ≠ \emptyset} \cap \hist = \emptyset: \hist, \ar_4 \ileadstoe \phi$.

\begin{definition}[Claim]
	$\exists k \in 2\N$ and a finite sequence $(\args_i)_{i \in 2\N, i ≤ k} \suchthat \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall i \in 2\N, i ≤ k, \forall \ar_i \in S_i: \ar_i$ defends $\phi$ under protection of $S_{i + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_i \subseteq \cup_{\ar_{i - 2} \in S_{i - 2}, \ar_{i - 1} \in \allargs} f(\ar_{i - 1}, \ar_{i - 2})$.
\end{definition}
Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its restriction.

No, rather: if $\ar_2$ can’t be defended, and $\ar'_2$ can’t either (all those attacking $\ar_1$, in fact), then $\ar_0$ is not necessary; thus some other $\ar'_0$ is enough. (Or is this equivalent?) Theimportant stuff is to anticipate attacks: if not $\ar_0$ decisive, then $\ar_1$ attacks $\ar_0$ and $\ar_2$ is decisive.

I need a condition of the form: $\forall i \suchthat …, \ar$ decisive. And the above claim is of that form (?): given $i$, either $\ar_0$ is decisive, or $\ar_1$ attacks it but then $\ar_2$ is decisive, …

\subsection{Conditions without history}
To verify or falsify these conditions, whether $(\ar_1, \ar_0) \ileadstoe \phi$ must be observable, but one may suspect that once $i$ has seen some $\ar$, then no more $(\ar_1, \ar_0) \ileadstoe \phi$ but that this does not imply that this would hold without $\ar$ for $i$. The general falsifiable claim is not clear.
